Model diagnostics

### 2025-04-04 notebook/model-definitions.qmd
Explain/illustrate marginal means as coefs
Clean up some notebook stuff

TODO: Formal math for the models

>>>>

## Formal math

$$
\begin{aligned}
&\ \textbf{Multinomial probability of selection of choice}_i \textbf{ in respondent}_j \\
\text{Choice}_{i_j} \sim&\ \operatorname{Categorical}(\{\mu_{1,i_j}, \mu_{2,i_j}, \mu_{3,i_j}\}) \\[10pt]
&\ \textbf{Model for probability of each option} \\
\{\mu_{1,i_j}, \mu_{2,i_j}, \mu_{3,i_j}\} =&\ (\beta_0 + b_{0_j}) + \beta_1 \text{Organization[Greenpeace]}_{i_j} + \beta_2 \text{Organization[Oxfam]}_{i_j} + \\
&\ \beta_3 \text{Organization[Red Cross]}_{i_j} + \beta_4 \text{Issue[Environment]}_{i_j} + \\
&\ \beta_5 \text{Issue[Human rights]}_{i_j} + \beta_6 \text{Issue[Refugee relief]}_{i_j} + \\
&\ \beta_7 \text{Transparency[Yes]}_{i_j} + \beta_8 \text{Accountability[Yes]}_{i_j} + \\
&\ \beta_9 \text{Funding[Few wealthy donors]}_{i_j} + \beta_{10} \text{Funding[Government grants]}_{i_j} + \\
&\ \beta_{11} \text{Government relationship[Criticized]}_{i_j} + \\
&\ \beta_{12} \text{Government relationship[Under crackdown]}_{i_j} \\[5pt]
b_{0_j} \sim&\ \mathcal{N}(0, \sigma_0) \qquad\quad\quad \text{Respondent-specific offsets from global probability} \\[10pt]
&\ \textbf{Priors} \\
\beta_{0 \dots 12} \sim&\ \mathcal{N} (0, 3) \qquad\qquad\ \ \text{Prior for choice-level coefficients} \\
\sigma_0 \sim&\ \operatorname{Exponential}(1) \quad \text{Prior for between-respondent variability}
\end{aligned}
$$

## R code

```{r}
#| eval: false
#| echo: true
#| code-fold: false
#| file: "../R/funs_models.R"
#| filename: "R/funs_models.R"
```

### 2025-04-04 notebook/model-diagnostics.qmd
Clean up some notebook stuff

These are histograms of the ranks of the parameter draws across the four chains. If the chains are exploring the same space efficiently, the histograms should be similar and overlapping and no one chain should have a specific rank for a long time [@McElreath:2020a, 284].

>>>>

These are histograms of the ranks of the parameter draws across the four chains. If the chains are exploring the same space efficiently, the histograms should be similar and overlapping and no one chain should have a specific rank for a long time [@McElreath:2020, 284].
